My title

### 2022-03-22 outputs/paper/paper.Rmd
added comment

```{r, include= FALSE}
myvars <- c("sex", "cip_10")
cip_based_on_gender <- input_csv[myvars]
cip_based_on_gender<-cip_based_on_gender[!cip_based_on_gender$cip_10>=6,]
cip_based_on_gender$sex[cip_based_on_gender$sex==2] <- "Female"
cip_based_on_gender$sex[cip_based_on_gender$sex==1] <- "Male"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==1] <- "Great confidence"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==2] <- "Some confidence"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==3] <- "Small confidence"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==4] <- "No confidence"

cip_count_based_on_gender <- table(cip_based_on_gender$sex, cip_based_on_gender$cip_10)

@@

```{r, include = FALSE}
myvars <- c("sex", "plp_130", "plp_140")
pip_based_on_gender <- input_csv[myvars]
pip_based_on_gender<-pip_based_on_gender[!(pip_based_on_gender$plp_130>=6 | pip_based_on_gender$plp_140>=6),]
pip_based_on_gender$sex[pip_based_on_gender$sex==2] <- "Female"
pip_based_on_gender$sex[pip_based_on_gender$sex==1] <- "Male"
pip_based_on_gender$plp_130[pip_based_on_gender$plp_130==1] <- "Good Job"
pip_based_on_gender$plp_130[pip_based_on_gender$plp_130==2] <- "Average Job"
pip_based_on_gender$plp_130[pip_based_on_gender$plp_130==3] <- "Poor Job"

@@

```{r, include = FALSE}
myvars <- c("sex", "pcc_145")
conf_in_court_based_on_gender <- input_csv[myvars]
conf_in_court_based_on_gender<-conf_in_court_based_on_gender[!(conf_in_court_based_on_gender$pcc_145>=6),]
conf_in_court_based_on_gender$sex[conf_in_court_based_on_gender$sex==2] <- "Female"
conf_in_court_based_on_gender$sex[conf_in_court_based_on_gender$sex==1] <- "Male"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==1] <- "Great Confidence"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==2] <- "Some Confidence"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==3] <- "Not Very Much Confidence"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==4] <- "No Confidence"

conf_in_court_based_on_gender <- table(conf_in_court_based_on_gender$sex, conf_in_court_based_on_gender$pcc_145)

>>>>

```{r, include= FALSE}
myvars <- c("sex", "cip_10")
cip_based_on_gender <- input_csv[myvars]
# Only interested in valid responses
cip_based_on_gender<-cip_based_on_gender[!cip_based_on_gender$cip_10>=6,]
# Rename column
cip_based_on_gender$sex[cip_based_on_gender$sex==2] <- "Female"
cip_based_on_gender$sex[cip_based_on_gender$sex==1] <- "Male"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==1] <- "Great confidence"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==2] <- "Some confidence"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==3] <- "Small confidence"
cip_based_on_gender$cip_10[cip_based_on_gender$cip_10==4] <- "No confidence"
# Generate table for plotting
cip_count_based_on_gender <- table(cip_based_on_gender$sex, cip_based_on_gender$cip_10)

@@

```{r, include = FALSE}
myvars <- c("sex", "plp_130", "plp_140")
pip_based_on_gender <- input_csv[myvars]
# Filter out valid response
pip_based_on_gender<-pip_based_on_gender[!(pip_based_on_gender$plp_130>=6 | pip_based_on_gender$plp_140>=6),]
# Rename column
pip_based_on_gender$sex[pip_based_on_gender$sex==2] <- "Female"
pip_based_on_gender$sex[pip_based_on_gender$sex==1] <- "Male"
pip_based_on_gender$plp_130[pip_based_on_gender$plp_130==1] <- "Good Job"
pip_based_on_gender$plp_130[pip_based_on_gender$plp_130==2] <- "Average Job"
pip_based_on_gender$plp_130[pip_based_on_gender$plp_130==3] <- "Poor Job"

@@

```{r, include = FALSE}
myvars <- c("sex", "pcc_145")
conf_in_court_based_on_gender <- input_csv[myvars]
# Filter out valid response
conf_in_court_based_on_gender<-conf_in_court_based_on_gender[!(conf_in_court_based_on_gender$pcc_145>=6),]
conf_in_court_based_on_gender$sex[conf_in_court_based_on_gender$sex==2] <- "Female"
conf_in_court_based_on_gender$sex[conf_in_court_based_on_gender$sex==1] <- "Male"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==1] <- "Great Confidence"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==2] <- "Some Confidence"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==3] <- "Not Very Much Confidence"
conf_in_court_based_on_gender$pcc_145[conf_in_court_based_on_gender$pcc_145==4] <- "No Confidence"
# Generate table
conf_in_court_based_on_gender <- table(conf_in_court_based_on_gender$sex, conf_in_court_based_on_gender$pcc_145)
